One Year HPC Certification Forum in Retrospective

### 2019-04-12 paper.tex
Further

\begin{document}
\title{Looking Back: One Year HPC Certification Forum}

@@

@@

>>>>

\begin{document}
\title{One Year HPC Certification Forum in Retrospective}

@@

The competences are organized in a tree that serves the purpose to organize and structure the skills from a coarse-grained to a fine-grained representation allowing users to browse the skill based on the semantics.
The root level of our current skill tree is shown in \Cref{skill-tree}.
The idea is that the skills from the root level provide an indication about their scope,
e.g., are they core knowledge, dealing with the usage of HPC environments, or about programming.
This should allow the user to rapidly drill into the skill representation.
On the leaf level, a skill is fine-grained -- we scope the level of detail here to be able to be taught in a 1.5 hour lecture up to a 4 hour workshop.

As the tree serves the purpose to organize the skills, there can also be references from one branch to a skill in another.
This import allows to reuse the definitions of the skills while still allowing users to navigate the tree according to the semantics.

\subsection{Description of a skill}

Each skill on the tree and even the inner nodes are described in more detail as follows:

\begin{itemize}
  \item \textbf{ID}: ID according the organization in the skill tree.
  \item \textbf{Name}: A speaking name for a skill.
  \item \textbf{Background}: Provides brief information motivating the need for the skill and how this skill fits into the skill map; what is the bigger picture.
  \item \textbf{Aims}:
  \jk{TODO}
  Programme or module aims serve as broad purposes or goals and are generally a statement of the intentions of the teacher or school when designing or running the course. They are not intended to be statements of what students will learn or do, but rather over-arching intentions of the course. At a basic level, aims are trying to answer two questions: What is the purpose of this programme or module? What is the programme or module trying to achieve? reference
  \item \textbf{Learning outcomes}: Defines briefly what what practitioners know / will learn. The objected are statements what prospect learners are able to do, they should
  describe or define an action be clearly stated be measurable/quantifiable to some extent, for example, by using action words.
\end{itemize}

The closer a skill is to the root, the more abstract it is defined, while leaf nodes cover the knowledge for the specific skill.

@@

The following skill describes a leaf-node for SLURM, note that it is expected to complement a generic skill that describes how the general workload management works in HPC.

\begin{itemize}
  \item \textbf{ID}: USE4.2.2-B
  \item \textbf{Name}: SLURM Workload manager
  \item \textbf{Background}: SLURM is a widely used open-source workload manager providing various advanced features.
  \item \textbf{Aims}:
  \begin{itemize}
    \item To enable practitioners to comprehend and describe the basic architecture of SLURM and the suite of tools.
    \item To use relevant tools to run and monitor (parallel) applications
  \end{itemize}
  \item \textbf{Learning outcomes}:
  \begin{itemize}
  \item run interactive jobs with salloc, a batch job with sbatch
  \item explain the architecture of SLURM, i.e., the role of slurmd, srun and the injection of environment variables
  \item explain the function of the tools: sacct, sbatch, salloc, srun, scancel, squeue, sinfo
  \item explain time limits and the benefit of a backfill scheduler
  \item comprehend that environment variables are set when running a job
  \item comprehend and describe the expected behavior of a simple job scripts
  \item comprehend how variables are prioritized when using command line and a script
  \item change a provided job template and embed them into shell scripts to run a variety of parallel applications
  \item analyze the output generated from submitting to the job scheduler and typically generated errors
  \end{itemize}
\end{itemize}

%\begin{itemize}
%  \item \textbf{Name}:
%  \item \textbf{Background}:
%  \item \textbf{Aim}:
%  \item \textbf{Learning outcomes}:
%\end{itemize}
